---
title: "IPRTemplate"
author: "International Planning & Research"
date: "February 9, 2018"
output:
  word_document:
    fig_height: 4
    fig_width: 5
    reference_docx: IPR_styles_reference-01.docx #( For IPR_styles_reference-02.docx, set fig_height: 3, set fig_width: 4)
    toc: yes
    toc_depth: 2
subtitle: Subtitle - IPRTemplate
---

```{r include=FALSE}

## IPR colors for ggplot2

#devtools::install_github('cttobin/ggthemr') 
#install.packages(c("ggplot2", "knitr") 

library(ggplot2);library(ggthemr);library(knitr)
source("IPR_color_select.R")
colors_IPR <- color_mono_10 # select your colors. (Choices: color_mono_4, color_mono_5, color_mono_7, color_mono_10)
source("IPR_ggthemr.R")
ggthemr(colortheme_IPR)

```


# 1. Overview

IPR Template IPR Template IPR Template IPR Template IPR Template IPR Template IPR Template IPR Template IPR Template IPR Template IPR Template IPR Template 

# 2. Analysis
## 2.1. Data Processing
IPR Template IPR Template IPR Template IPR Template IPR Template IPR Template IPR Template IPR Template IPR Template IPR Template IPR Template IPR Template 


```{r Data Processing}
data(iris)
knitr::kable(head(iris))

```


## 2.2. Modeling
IPR Template IPR Template IPR Template IPR Template IPR Template IPR Template IPR Template IPR Template IPR Template IPR Template IPR Template IPR Template 

```{r Modeling}
model <- lm(Sepal.Length ~ Petal.Width, data = iris)
summary(model)

```

## 2.3. Visualization

```{r echo = FALSE}

ggplot(iris, aes(x = Petal.Width, y = Sepal.Length, color = Species)) + 
  geom_point() +
  stat_smooth(method = "lm")

```

# 3. Conclusion
IPR Template IPR Template IPR Template IPR Template IPR Template IPR Template IPR Template IPR Template IPR Template IPR Template IPR Template IPR Template 



